\documentclass[10pt,-letter paper]{article}
\usepackage[left=1in, right=0.75in, top=1in, bottom=0.75in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\newcommand{\sgn}{\mathop{\mathrm{sgn}}}
\providecommand{\abs}[1]{\left\vert#1\right\vert}
\providecommand{\res}[1]{\Res\displaylimits_{#1}} 
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
%\providecommand{\norm}[1]{\lVert#1\rVert}
\providecommand{\mtx}[1]{\mathbf{#1}}
\providecommand{\mean}[1]{E\left[ #1 \right]}
\providecommand{\fourier}{\overset{\mathcal{F}}{ \rightleftharpoons}}
%\providecommand{\hilbert}{\overset{\mathcal{H}}{ \rightleftharpoons}}
\providecommand{\system}{\overset{\mathcal{H}}{ \longleftrightarrow}}
 %\newcommand{\solution}[2]{\textbf{Solution:}{#1}}
%\newcommand{\solution}{\noindent \textbf{Solution: }}
\newcommand{\cosec}{\,\text{cosec}\,}
\providecommand{\dec}[2]{\ensuremath{\overset{#1}{\underset{#2}{\gtrless}}}}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\newcommand{\myaugvec}[2]{\ensuremath{\begin{amatrix}{#1}#2\end{amatrix}}}
\newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\title{MATHEMATICS}
\author{SECTION A}
\date{\today}
\begin{document}

\maketitle

\begin{enumerate}

\item Find the angle between the line $\overrightarrow{r}=\brak{2\hat{i}-\hat{j}+3\hat{k}}+\lambda\brak{3\hat{i}-\hat{j}+2\hat{k}}$ and the plane $\overrightarrow{r}.\brak{\hat{i}+\hat{j}+\hat{k}}=3$.

\item Find the co-ordinates of the point, where the line $\frac{x+2}{1}=\frac{y-5}{3}=\frac{z+1}{5}$ cuts the yz-plane.

\item If $y=5e^{7x}+6e^{-7x}$, show that $\frac{d^2{y}}{d{x^2}}=49y$.

\item If $A$ is a square matrix of order $2$ and $\mydet{A}$ = $4$, then find the value of $\mydet{2\cdot AA'}$, where $A'$ is the transpose of matrix $A$.

\item Find the order of the differential equation of the family of circles of radius $3$ units.

\item Find the value of $\brak{x-y}$ from the matrix equation $2\myvec{x & 5 \\ 7 & y-3} + \myvec{-3 & -4 \\ 1 & 2}= \myvec{7 & 6 \\ 15 & 14}$.

\item Solve the following differential equation :
\begin{align*}\brak{y + 3x^{2}}\frac{dx}{dy}=x
\end{align*}

\item Find:
\begin{align*}\int e^x\brak{\cos x-\sin x}\cosec^2 x dx
\end{align*}

\item Using vectors, prove that the points $\brak{2,-1,3},\brak{3,-5,1}$ and $\brak{-1,11,9}$ are collinear.

\item For any two vectors $\overrightarrow{a}$ and $\overrightarrow{b}$, prove that\begin{align*}\brak{{\overrightarrow{a} \times \overrightarrow{b}}}^2 =\overrightarrow{a}^2\overrightarrow{b}^2 - \brak{{\overrightarrow{a} \cdot \overrightarrow{b}}}^2\end{align*}

\item Find:
\begin{align*}\int\frac{x-1}{\brak{x-2}\brak{x-3}}dx
\end{align*}

\item Integrate:
\begin{align*}\frac{e^x}{\sqrt{5-4e^x-e^{2x}}}
\end{align*} with respect to x.

\item If $P\brak{A} =0.6, P\brak{B} =0.5$and$P\brak{B\mid A} =0.4$, find $P\brak{A\cup B}$and$P\brak{A\mid B}$.

\item If an operation $\ast$ on the set of integers Z is defined by $a \ast b = 2a^{2}+b,$ then find
\begin{enumerate}
\item whether it is a binary or not, and
\item if a binary, then is it commutative or not.
\end{enumerate}

\item Four cards are drawn one by one with replacement from a well-shuffled deck of playing cards. Find the probability that at least three cards are of diamonds.

\item The probability of two students $A$ and $B$ coming to school on time are $\frac{2}{7}$ and $\frac{4}{7}$, respectively. Assuming that the events '$A$ coming on time' and '$B$ coming on time' are independent, find the probability of only one of them coming to school on time.

\item If $x^{p}y^{q}=\brak{x+y}^{p+q}$, prove that $\frac{dy}{dx}=\frac{y}{x}$, and $\frac{d^2{y}}{d{x^2}}=0$.

\item Find:
\begin{align*}\int \brak{\sin x.\sin 2x. sin 3x}dx
\end{align*}

\item Differentiate $\tan^{-1}\frac{3x-{x^3}}{1-3x^2},\vert{x}\vert<\frac{1}{\sqrt{3}}$w.r.t. $\tan^{-1}\frac{x}{\sqrt{1-x^2}}$.

\item If $\sqrt{1-x^2}+\sqrt{1-y^2}=a\brak{x-y},\vert{x}\vert<1,\vert{y}\vert <1$,show that $\frac{dy}{dx}=\sqrt{\frac{1-y^2}{1-x^2}}$.

\item Find the particular solution of the differential equation: $\brak{1+e^{2x}}{dy}+\brak{1+y^2}{e^{x}dx}=0$, given that $y\brak0=1$.

\item Find the particular solution of the differential equation: $x\frac{dy}{dx}\sin\brak{\frac{y}{x}}+x-y\sin\brak{\frac{y}{x}}=0$,given that $y\brak1=\frac{\pi}{2}$.

\item Prove that the relation $\mathbf{R}$ in the set $A = \cbrak{1,2,3,4,5,6,7}$ given by $\mathbf{R}=\cbrak{a,b}:\mydet{a-b}\text {is even }$ is an equivalence relation.

\item Show that the function f in $A = R-\{\frac{2}{3}\}$ defined as $f\brak{x} = \frac{4x+3}{6x-4}$ is one-one and onto. Hence, find $f^{-1}$.

\item Find whether the function $f\brak{x}=\cos \brak{{2x}+{\frac{\pi}{4}}}$; is increasing or decreasing in the interval $\frac{3\pi}{8}<x<\frac{5\pi}{8}$.

\item Find the equation of the plane passing through $\brak{-1,3,2}$ and perpendicular to the planes $x+2y+3z=5$ and $3x+3y+z=0$.

\item Prove that :\begin{align*}\sin^{-1}\frac{4}{5}+\tan^{-1}\frac{5}{12}+\cos^{-1}\frac{63}{65}=\frac{\pi}{2}\end{align*}

\item Evaluate :\begin{align*}\int_{1}^{5} \brak{\vert{x-1}\vert+\vert{x-2}\vert+\vert{x-4}\vert} dx\end{align*}

\item Using vectors, find the value of $x$ such that the four points $A$ $\brak{x,5,-1}$,$B$ $\brak{3,2,1}$,$C$ $\brak{4,5,5}$ and $D$ $\brak{4,2,-2}$ are coplanar.

\item If $x$, $y$, $z$ are different and $\Delta=\mydet{x & x^2 & x^3 -1\\y & y^2 & y^3 -1\\z & z^2 & z^3 -1} = 0$ ,then using properties of determinants, show that $xyz = 1$.

\item Using integration, find the area of the following region :
\begin{align*}\{\brak{x,y} :x^2+y^2\leq16a^2~and~y^2\leq6ax\}
\end{align*}

\item Using integration, find the area of triangle $ABC$ bounded by the lines 
\begin{align*}4x-y+5=0, x+y-5=0~and~x-4y+5=0.
\end{align*}

\item Find the vector equation of the line passing through$\brak{2,1,-1}$ and parallel to the line $\overrightarrow{r}=\brak{\hat{i}+\hat{j}}+\lambda\brak{2\hat{i}-\hat{j}+\hat{k}}$.Also, find the distance between these two lines.

\item Find the coordinates of the foot $Q$ of the perpendicular drawn from the point $P\brak{1,3,4}$ to the plane $2x-y+z+3=0$. Find the distance $PQ$ and the image of $P$ treating the planes as a mirror.

\item A company manufactures two types of novelty souvenirs made of plywood. Souvenirs of type $A$ require $5$ minutes each for cutting and $10$ minutes each for assembling. Souvenirs of type $B$ require $8$ minutes each for cutting and $8$ minutes each for assembling. There are $3$ hours $20$ minutes available for cutting and $4$ hours for assembling. The profit for type A souvenirs is $\rupee~100$ each and for type $B$ souvenirs, profit is $\rupee~120$ each.How many souvenirs of each type should the company manufacture in order to maximise the profit? Formulate the problem as a LPP and then solve it graphically.

\item In answering a question on a multiple choice questions test with four choices in each questions, out of which only one is correct, a student either guesses or copies or knows the answer. The probability that he makes a guess is $\frac{1}{4}$ and the probability the he copies is also $\frac{1}{4}$. The probability that the answer is correct, given that he copied it is $\frac{3}{4}$. Find the probabiliy that he knows the answer to the question, given that  he correctly answered it.

\item An isosceles triangle of verticle angle $2\Theta$ is inscribed in a circle of radius $a$. show that the area of the triangle is maximum when $\Theta=\frac{\pi}{6}$.

\item Using elementary row transformations, find the inverse of the matrix $\myvec{3 & 0 & -1\\2 & 3 & 0\\0 & 4 & 1\\}$.

\item Using matrices, solve the following system of linear equations:\begin{align*}2x+3y+10z=4\\4x-6y+5z=1\\6x+9y-20z=2\end{align*}

\end{enumerate}
\end{document}
